Incremental Forward Reasoning for White-Box~Proof~Search

### 2025-02-25 paper.tex
update tests (without precomp)

\begin{figure}
  \centering
  \begin{subfigure}[b]{.5\textwidth}
    \centering
    \begin{tikzpicture}[scale=0.75]
      \begin{axis}[
        xlabel={Number of hypotheses},
        ylabel={Time in ms},
        xmin=1, xmax=32,
        ymin=4, ymax=2^16,
        %xtick={1,2,4,8,16},
        %ytick={2^3,2^5,2^7,2^9,2^11,2^13},
        xmode=log,
        ymode=log,
        log basis x=2,
        log basis y=2,
        legend pos=north west,
        ymajorgrids=true,
        grid style=dashed,
        legend image post style={mark=}
        ]
        \addplot[
          color=orange,
          mark=square,
          style=densely dashed,
          mark options={style={solid}}
          ]
          coordinates {
            (1, 7.663472) (2, 9.354750) (4, 15.768194) (8, 104.921791) (16, 1882.683111) (32, 45220.919667)  
          };
        \addplot[
          color=blue,
          mark=square,
          ]
          coordinates {
            (1, 10.308541) (2, 10.704638) (4, 16.274305) (8, 38.800833) (16, 179.697681) (32, 1175.888750)
          };
        \addplot[
          color=orange,
          mark=o,
          style=densely dashed,
          mark options={style={solid}}
          ]
          coordinates {
            (1, 10.591138) (2, 23.881333) (4, 142.013389) (8, 1676.148375) (16, 24327.359417) (32, 392049.849708) 
          };
        \addplot[
          color=blue,
          mark=o,
          ]
          coordinates {
            (1, 13.974694) (2, 26.216833) (4, 68.953444) (8, 245.601028) (16, 1028.670680) (32, 4388.917500) 
          };
      \end{axis}
    \end{tikzpicture}
    \caption{Transitivity benchmark}%
    \label{fig:trans}
  \end{subfigure}%
  \begin{subfigure}[b]{.5\textwidth}
    \centering
    \begin{tikzpicture}[scale=0.75]
      \begin{axis}[
        xlabel={Number of rules},
        %ylabel={Time in ms},
        xmin=1, xmax=32,
        ymin=4, ymax=2^16,
        ymode=log,xmode=log,
        log basis x=2,
        log basis y=2,
        legend pos=north west,
        ymajorgrids=true,
        grid style=dashed,
        legend image post style={mark=},
        ]
        \addplot[
          color=orange,
          mark=square,
          style=densely dashed,
          mark options={style={solid}}
          ]
          coordinates {
            (1, 10.399958) (2, 16.426541) (4, 43.461403) (8, 205.595541) (16, 1238.090889) (32, 8927.857819)
          };
          \addlegendentry{naive}
        \addplot[
          color=blue,
          mark=square,
          ]
          coordinates {
            (1, 11.231875) (2, 12.879500) (4, 16.851930) (8, 24.666485) (16, 42.054055) (32, 76.369778)
          };
          \addlegendentry{incremental}
        \addplot[
          color=orange,
          mark=o,
          style=densely dashed,
          mark options={style={solid}}
          ]
          coordinates {
            (1, 19.405222) (2, 33.487472) (4, 80.107597) (8, 284.954791) (16, 1536.089624) (32, 10721.729861)
          };
        \addplot[
          color=blue,
          mark=o,
          ]
          coordinates {
            (1, 25.892069) (2, 40.031930) (4, 69.446902) (8, 130.640986) (16, 260.653917) (32, 481.827902)
          };
      \end{axis}
    \end{tikzpicture}
    \caption{Independence benchmark}%
    \label{fig:indep}
  \end{subfigure}
  \caption{Results of the transitivity (\subref{fig:trans}) and independence (\subref{fig:indep}) benchmarks for $a = 0$ (\protect\showpgfsquare) and $a = 100$ (\protect\showpgfcircle).}%
  \label{fig:benchmark}
  \end{figure}

@@

\begin{figure}
  \centering
  \begin{subfigure}{.5\textwidth}
    \centering
    \begin{tikzpicture}[scale=0.75]
      \begin{axis}[
        xlabel={Depth},
        ylabel={Time in ms},
        xmin=1, xmax=5,
        ymin=8, ymax=2^10,
        xtick={1,2,3,4,5},
        ymode=log,
        log basis y=2,
        ymajorgrids=true,
        grid style=dashed
        ]
        \addplot[
          color=orange,
          mark=square,
          style=densely dashed,
          mark options={style={solid}}
          ]
          coordinates {
            (1, 35.466292) (2, 40.918638) (3, 46.936125) (4, 54.933124) (5, 61.269861)
          };
        \addplot[
          color=blue,
          mark=square,
          ]
          coordinates {
            (1, 135.967736) (2, 127.324444) (3, 136.891250) (4, 118.720444) (5, 116.293222)
          };
        \addplot[
          color=orange,
          mark=o,
          style=densely dashed,
          mark options={style={solid}}
          ]
          coordinates {
            (1, 107.978069) (2, 115.900527) (3, 122.454958) (4, 137.732764) (5, 144.037681)
          };
        \addplot[
          color=blue,
          mark=o,
          ]
          coordinates {
            (1, 619.932611) (2, 601.456805) (3, 600.926110) (4, 589.144389) (5, 595.091180)
          };
      \end{axis}
    \end{tikzpicture}
    \caption{Without precompilation}%
    \label{fig:erase-noprecomp}
  \end{subfigure}%
  \begin{subfigure}{.5\textwidth}
    \centering
    \begin{tikzpicture}[scale=0.75]
      \begin{axis}[
        xlabel={Depth},
        xmin=1, xmax=5,
        ymin=8, ymax=1024,
        xtick={1,2,3,4,5},
        ymode=log,
        log basis y=2,
        %yticklabels={},
        legend pos=north west,
        ymajorgrids=true,
        grid style=dashed,
        legend image post style={mark=},
        ]
        \addplot[
          color=orange,
          mark=square,
          style=densely dashed,
          mark options={style={solid}}
          ]
          coordinates {
            (1, 13.728805) (2, 17.909194) (3, 23.324666) (4, 28.030819) (5, 33.279611)
          };
        \addlegendentry{naive}
        \addplot[
          color=blue,
          mark=square,
          ]
          coordinates {
            (1, 13.841305) (2, 12.801791) (3, 13.358389) (4, 13.200611) (5, 13.251902)
          };
        \addlegendentry{incremental}
        \addplot[
          color=orange,
          mark=o,
          style=densely dashed,
          mark options={style={solid}}
          ]
          coordinates {
            (1, 81.546486) (2, 85.345444) (3, 90.532347) (4, 98.247764) (5, 105.423875)
          };
        \addplot[
          color=blue,
          mark=o,
          ]
          coordinates {
            (1, 25.539097) (2, 24.432485) (3, 25.629666) (4, 23.935250) (5, 23.911139)
          };
      \end{axis}
    \end{tikzpicture}
    \caption{With precompilation}%
    \label{fig:erase-precomp}
  \end{subfigure}
  \caption{Results of the depth benchmark for $n = 6$ with precompilation disabled (\subref{fig:erase-noprecomp}) or enabled (\subref{fig:erase-precomp}) and with $a = 0$ (\protect\showpgfsquare) or $a = 100$ (\protect\showpgfcircle).}%
  \label{fig:erase}
\end{figure}

>>>>

\begin{figure}
  \centering
  \begin{subfigure}[b]{.5\textwidth}
    \centering
    \begin{tikzpicture}[scale=0.75]
      \begin{axis}[
        xlabel={Number of hypotheses},
        ylabel={Time in ms},
        xmin=1, xmax=32,
        ymin=4, ymax=2^16,
        %xtick={1,2,4,8,16},
        %ytick={2^3,2^5,2^7,2^9,2^11,2^13},
        xmode=log,
        ymode=log,
        log basis x=2,
        log basis y=2,
        legend pos=north west,
        ymajorgrids=true,
        grid style=dashed,
        legend image post style={mark=}
        ]
        \addplot[
          color=orange,
          mark=square,
          style=densely dashed,
          mark options={style={solid}}
          ]
          coordinates {
            (1, 6.133137) (2, 7.651537) (4, 13.290939) (8, 91.869091) (16, 1718.359150) (32, 43017.778968) 
          };
        \addplot[
          color=blue,
          mark=square,
          ]
          coordinates {
            (1, 7.088877) (2, 9.455166) (4, 13.889670) (8, 33.293693) (16, 153.769004) (32, 1018.813208)
          };
        \addplot[
          color=orange,
          mark=o,
          style=densely dashed,
          mark options={style={solid}}
          ]
          coordinates {
            (1, 8.589029) (2, 19.014450) (4, 126.356247) (8, 1560.866835) (16, 22985.414025) (32, 373397.722281) 
          };
        \addplot[
          color=blue,
          mark=o,
          ]
          coordinates {
            (1, 11.729506) (2, 22.231345) (4, 58.294695) (8, 207.863068) (16, 888.210662) (32, 3804.700212)
          };
      \end{axis}
    \end{tikzpicture}
    \caption{Transitivity benchmark}%
    \label{fig:trans}
  \end{subfigure}%
  \begin{subfigure}[b]{.5\textwidth}
    \centering
    \begin{tikzpicture}[scale=0.75]
      \begin{axis}[
        xlabel={Number of rules},
        %ylabel={Time in ms},
        xmin=1, xmax=32,
        ymin=4, ymax=2^16,
        ymode=log,xmode=log,
        log basis x=2,
        log basis y=2,
        legend pos=north west,
        ymajorgrids=true,
        grid style=dashed,
        legend image post style={mark=},
        ]
        \addplot[
          color=orange,
          mark=square,
          style=densely dashed,
          mark options={style={solid}}
          ]
          coordinates {
            (1, 8.481945) (2, 13.017566) (4, 36.759979) (8, 180.629616) (16, 1156.813791) (32, 8343.946414)
          };
          \addlegendentry{naive}
        \addplot[
          color=blue,
          mark=square,
          ]
          coordinates {
            (1, 10.116120) (2, 11.520718) (4, 14.605806) (8, 21.079808) (16, 34.858708) (32, 64.986725)
          };
          \addlegendentry{incremental}
        \addplot[
          color=orange,
          mark=o,
          style=densely dashed,
          mark options={style={solid}}
          ]
          coordinates {
            (1, 13.743712) (2, 23.221681) (4, 58.603629) (8, 235.183885) (16, 1389.365902) (32, 9687.141454) 
          };
        \addplot[
          color=blue,
          mark=o,
          ]
          coordinates {
            (1, 19.886189) (2, 30.294954) (4, 51.187760) (8, 93.739397) (16, 178.442899) (32, 351.595918)
          };
      \end{axis}
    \end{tikzpicture}
    \caption{Independence benchmark}%
    \label{fig:indep}
  \end{subfigure}
  \caption{Results of the transitivity (\subref{fig:trans}) and independence (\subref{fig:indep}) benchmarks for $a = 0$ (\protect\showpgfsquare) and $a = 100$ (\protect\showpgfcircle).}%
  \label{fig:benchmark}
  \end{figure}

@@

\begin{figure}
  \centering
  \begin{subfigure}{.5\textwidth}
    \centering
    \begin{tikzpicture}[scale=0.75]
      \begin{axis}[
        xlabel={Depth},
        ylabel={Time in ms},
        xmin=1, xmax=5,
        ymin=8, ymax=2^10,
        xtick={1,2,3,4,5},
        ymode=log,
        log basis y=2,
        ymajorgrids=true,
        grid style=dashed
        ]
        \addplot[
          color=orange,
          mark=square,
          style=densely dashed,
          mark options={style={solid}}
          ]
          coordinates {
            (1, 29.953518) (2, 36.796839) (3, 43.879808) (4, 50.748666) (5, 57.841152) 
          };
        \addplot[
          color=blue,
          mark=square,
          ]
          coordinates {
            (1, 130.215285) (2, 115.646322) (3, 125.256110) (4, 111.167837) (5, 110.668739)
          };
        \addplot[
          color=orange,
          mark=o,
          style=densely dashed,
          mark options={style={solid}}
          ]
          coordinates {
            (1, 99.132787) (2, 106.834506) (3, 114.863343) (4, 122.601670) (5, 130.616379) 
          };
        \addplot[
          color=blue,
          mark=o,
          ]
          coordinates {
            (1, 573.555837) (2, 559.131666) (3, 568.973041) (4, 550.852189) (5, 551.364258)
          };
      \end{axis}
    \end{tikzpicture}
    \caption{Without precompilation}%
    \label{fig:erase-noprecomp}
  \end{subfigure}%
  \begin{subfigure}{.5\textwidth}
    \centering
    \begin{tikzpicture}[scale=0.75]
      \begin{axis}[
        xlabel={Depth},
        xmin=1, xmax=5,
        ymin=8, ymax=1024,
        xtick={1,2,3,4,5},
        ymode=log,
        log basis y=2,
        %yticklabels={},
        legend pos=north west,
        ymajorgrids=true,
        grid style=dashed,
        legend image post style={mark=},
        ]
        \addplot[
          color=orange,
          mark=square,
          style=densely dashed,
          mark options={style={solid}}
          ]
          coordinates {
            (1, 13.728805) (2, 17.909194) (3, 23.324666) (4, 28.030819) (5, 33.279611)
          };
        \addlegendentry{naive}
        \addplot[
          color=blue,
          mark=square,
          ]
          coordinates {
            (1, 13.841305) (2, 12.801791) (3, 13.358389) (4, 13.200611) (5, 13.251902)
          };
        \addlegendentry{incremental}
        \addplot[
          color=orange,
          mark=o,
          style=densely dashed,
          mark options={style={solid}}
          ]
          coordinates {
            (1, 81.546486) (2, 85.345444) (3, 90.532347) (4, 98.247764) (5, 105.423875)
          };
        \addplot[
          color=blue,
          mark=o,
          ]
          coordinates {
            (1, 25.539097) (2, 24.432485) (3, 25.629666) (4, 23.935250) (5, 23.911139)
          };
      \end{axis}
    \end{tikzpicture}
    \caption{With precompilation}%
    \label{fig:erase-precomp}
  \end{subfigure}
  \caption{Results of the depth benchmark for $n = 6$ with precompilation disabled (\subref{fig:erase-noprecomp}) or enabled (\subref{fig:erase-precomp}) and with $a = 0$ (\protect\showpgfsquare) or $a = 100$ (\protect\showpgfcircle).}%
  \label{fig:erase}
\end{figure}
